The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2011-11-11 smurf_paper.tex
Add a couple of comments to sections.

@@

@@

@@

@@

@@

>>>>

\textit{May want to note that the pipeline is discussed elsewhere,
  e.g. Gibb et al 2006.}

@@

\textit{There are also the popped bolometers that could help fill the
gaps.}

@@

\textit{Surely flatfields are discussed in the main SCUBA-2 paper so
don't really have any useful purpose here since they aren't
technically part of the map-maker.}

@@

\textit{And matched filter is discussed here or superceded by
the 2D FFTs?}

@@

\textit{Or now an externally supplied mask.}

@@

\textit{Presumably the standard telescope acknowledgment here plus a thank you
to CFI for funding the DR work. Ed should probably thank both CANFAR
and JAC for additionally funding although his JAC funding is noted in
the affiliation.}
